### 2018-04-17 paper/algorithm.tex
Fixes Syntastic warnings

On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
We call this part of the protocol the \localoverlay, and present it in section~\ref{local overlay}. 
On the other hand, user's collectively upload the list of their connected devices and associated future predictions to a Distributed Hash Table (DHT): it serves as a registry of online peers (including connection probabilities for the next turn), and for the routing of files.
We describe this \globaloverlay in section~\ref{global overlay}. 
File exchange between two users is enabled by the two previous protocols, and is covered in section~\ref{file exchange}

@@

A user's devices, \(D_i\), use the \localoverlay to:
\begin{enumerate}
	\item Share information about the user's behavior.
	Devices use it to build a behavioral model and infer their future connection probability;
	\item Share files location \commentAL{Maybe...}
\end{enumerate}

\subsubsection{Sharing the user's behavior} % (fold)
\label{ssub:sharing_the_user_s_behavior}

Each device initially only knows when it is connected. 
To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
To do so, they employ a probabilistic dissemination protocol, based on previous work from our team \cite{luxey:hal-01704172}.
This algorithm, called \textsc{Sprinkler}, allows devices to gossip any new connection information to random peers, ensuring that all devices know the full observation sequence with a very high probability.
\textsc{Sprinkler} has shown resilient to devices churn \cite{luxey:cascade}, and is thus perfectly suited for our purpose, where a user's devices often disconnect and reconnect.

\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in section~\ref{sec:user_model}.}

@@

\subsubsection{Sharing files location} % (fold)
\label{ssub:sharing_files_location}

@@

Every device in the system participates in a Distributed Hash Table (DHT) that is used for two purposes:
\begin{enumerate}
	\item Providing routing information to nodes during file exchange. This is discussed in-depth in section~\ref{file exchange};
	\item Listing online devices and their probability of being online next time step.
\end{enumerate}

@@

In other words, \name must guarantee \emph{sender-receiver anonymity}.
To achieve this, communications go through onion routes, using rendez-vous points.
Our approach is tightly based on the Tor seminal paper \cite{Tor}.

\subsubsection{File exchange process} % (fold)
\label{ssub:file_exchange_process}

@@

\subsubsection{Onion routes in face of churn} % (fold)
\label{ssub:onion_routes_in_face_of_churn}

>>>>

On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
We call this part of the protocol the \localoverlay, and present it in 
\cref{local overlay}. On the other hand, user's collectively upload the list of 
their connected devices and associated future predictions to a Distributed Hash 
Table (DHT): it serves as a registry of online peers (including connection 
probabilities for the next turn), and for the routing of files.
We describe this \globaloverlay in \cref{global overlay}. File exchange between 
two users is enabled by the two previous protocols, and is covered in \cref{file 
  exchange}

@@

A user's devices, \(D_i\), use the \localoverlay to:
\begin{enumerate}
	\item Share information about the user's behavior.
	Devices use it to build a behavioral model and infer their future connection probability;
  \item Share files location \commentAL{Maybe \dots}
\end{enumerate}

\subsubsection{Sharing the user's behavior}% (fold)
\label{ssub:sharing_the_user_s_behavior}

Each device initially only knows when it is connected. 
To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
To do so, they employ a probabilistic dissemination protocol, based on previous work from our team~\cite{luxey:hal-01704172}.
This algorithm, called \textsc{Sprinkler}, allows devices to gossip any new connection information to random peers, ensuring that all devices know the full observation sequence with a very high probability.
\textsc{Sprinkler} has shown resilient to devices churn~\cite{luxey:cascade}, and is thus perfectly suited for our purpose, where a user's devices often disconnect and reconnect.

\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
  \cref{sec:user_model}.}

@@

\subsubsection{Sharing files location}% (fold)
\label{ssub:sharing_files_location}

@@

Every device in the system participates in a Distributed Hash Table (DHT) that is used for two purposes:
\begin{enumerate}
  \item Providing routing information to nodes during file exchange. This is 
    discussed in-depth in \cref{file exchange};
	\item Listing online devices and their probability of being online next time step.
\end{enumerate}

@@

In other words, \name must guarantee \emph{sender-receiver anonymity}.
To achieve this, communications go through onion routes, using rendez-vous points.
Our approach is tightly based on the Tor seminal paper~\cite{Tor}.

\subsubsection{File exchange process}% (fold)
\label{ssub:file_exchange_process}

@@

\subsubsection{Onion routes in face of churn}% (fold)
\label{ssub:onion_routes_in_face_of_churn}
